\papertitle

### 2021-03-12 source_separation/paper/paper.tex
Minor fixes

	We test the effectiveness of five difference source separation methods, both supervised and unsupervised, on 300 custom made targets that are combinations of sounds from different databases. During testing, a target is input to a source separation method, which outputs four sub-targets. Then each sub-target is independently orchestrated with a randomly assigned subset of the full orchestra. These orchestrations are then combined to play simultaneously, creating a final orchestrated solution. Then the distance between the target and solution is calculated, giving us a metric to compare the various separation methods. The random split of the orchestra is the same for each separation method of the same target.

@@

			This version of Conv-Tasnet, called \textbf{TDCN++}, was improved by \cite{tdcnpp} in order to be used for general sound separation, and not only for speech. The main architecture remains the same as in \cite{tdcn}, and the changes only affect the masking network. More specifically, feature-wise normalization replaces global normalization, residual connection ranges are extended to improve the flow of information, and learnable scale parameters are introduced to weight the outputs of each residual layer. Those modifications help the model to better extract features without drastically increasing its size.
			TDCN++ presents the interesting property of having almost the same architecture as TDCN but trained with generic sounds. Thus, it should naturally be better suited for our task, and the comparison between those two models in particular can give good insights about the impact of the data used for training.

@@

		\begin{figure}[t]
			\centering
				\includegraphics[width=\columnwidth]{figures/evaluation_diagram.png}
				\caption{Diagram showing the evaluation method. Note that in both orchestrations with split orchestra, the split is the same.}\label{fig:full_diagram}
		\end{figure}

>>>>

	We test the effectiveness of five difference source separation methods, both supervised and unsupervised, on 300 custom made targets that are combinations of sounds from different databases. During testing, a target is input to a source separation method, which outputs four sub-targets. Then each sub-target is independently orchestrated with a randomly assigned subset of the full orchestra. These orchestrations are then combined to play simultaneously, creating a final orchestrated solution. Then the distance between the target and solution is calculated, giving us a metric to compare the various separation methods. The random split of the orchestra is the same for each separation method of the same target. See Figure \ref{fig:eval_diagram} for a diagram of this process.

@@

			\textbf{TDCN++}, a version of Conv-Tasnet, was improved by \cite{tdcnpp} in order to be used for general sound separation, and not only for speech. The main architecture remains the same as in \cite{tdcn}, and the changes only affect the masking network. More specifically, feature-wise normalization replaces global normalization, residual connection ranges are extended to improve the flow of information, and learnable scale parameters are introduced to weight the outputs of each residual layer. Those modifications help the model to better extract features without drastically increasing its size.
			TDCN++ presents the interesting property of having almost the same architecture as TDCN but trained with generic sounds. Thus, it should naturally be better suited for our task, and the comparison between those two models in particular can give good insights about the impact of the data used for training.

@@

		\begin{figure}[t]
			\centering
				\includegraphics[width=\columnwidth]{figures/evaluation_diagram.png}
				\caption{Diagram showing the testing method. Note that in both orchestrations that use a split orchestra, the split is the same.}\label{fig:eval_diagram}
		\end{figure}
